---
title: "Example Report ACME Telephone ABT"
author: "Felipe Ortega"
date: "5/7/2020"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(partykit)
library(rpart)
library(rpart.plot)
```

# Model variables

**Input variables** for the models are:

* `avgrecurringCharge`: Average value of recurring bill charge to company clients.
* `avgOverBundleMins`: Excess of minutes in calls over the max. value allowed in
current service plan for this client.
* `binary_billAmountChangePct`: Binary tag checking whether the percentage change
in total bill amount with respec to to previous month is `positive` or `negative`.
* `lastMonthCustomerCareCalls`: Number of calls from client to customer care
service over the last month.
* `peakOffPeakRatio`: Ratio between peak and off-peak calls for this customer in
this month.
* `smartPhone`: Binary tag, checking whether the client has a smartphone (`TRUE`)
or not (`FALSE`).

**Output variable** is `churn`, tagging clients as kept (`0`) or gone (`1`).

# First decision tree model

```{r ctree-model, fig.cap="First classification tree."}
ctree_acme = readRDS(here("output", "models", "ctree_acme.rds"))

print(ctree_acme)
plot(ctree_acme, gp = gpar(fontsize = 10),
     inner_panel=node_inner,
     ip_args=list(
       abbreviate = TRUE, 
       id = FALSE)
)
```


# Second decision tree model

```{r rpart-tree, fig.cap="Second classification tree."}
rpart_acme = readRDS(here("output", "models", "rpart_acme.rds"))

summary(rpart_acme)
rpart.plot(rpart_acme)
```

